Implementation of a Brute Force Attack on A5/1 Cryptographical Algorithm in a GPU-based Volunteering Computing Project

### 2017-02-02 Paper PaCT 2017/paper.tex
+ Section 4 complete

\begin{table} \caption{(LOP3.LUT is a special instruction that implements
	arbitrary bitwise arity 3 functions in hardware. We use it as a substitute
	for the "bitselect" instruction.)} 
	\label{tab:gpuspeed} Performance of the different implementations of the
	Anderson's attack (search space is $2^{53}$) on a CPU and a GPU, measured
	in millions of key checks per second.  
	\begin {center} \begin{tabular} {| l | l | l | l |} \hline Computational
		device & Bit-slicing & LFSR precomputation \cite{BSW} \\ \hline CPU
		Intel Core I7 930 & 37 & 7 \\ \hline GPU NVIDIA GTX 1050 Ti & 9180 &
		483 \\ \hline GPU NVIDIA GTX 1050 Ti (LOP3.LUT) & 11950 & - \\ \hline

	\end{tabular}
\end {center}
\end{table}

@@

>>>>

\begin{table} \caption{(LOP3.LUT is a special instruction that implements
	arbitrary bitwise arity 3 functions in hardware. We use it as a substitute
	for the "bitselect" instruction.)} 
	\label{tab:gpuspeed} Performance of the different implementations of the
	Anderson's attack (search space is $2^{53}$) on a CPU and a GPU, measured
	in millions of key checks per second.  
	\begin {center} 
	\begin{tabular} {| l | l | l |} \hline Computational device & Bit-slicing &
		LFSR precomputation \cite{BSW} \\ \hline CPU Intel Core I7 930 & 37 & 7
		\\ \hline GPU NVIDIA GTX 1050 Ti & 9180 & 483 \\ \hline GPU NVIDIA GTX
		1050 Ti (LOP3.LUT) & 11950 & - \\ \hline
	\end{tabular}
\end {center}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation of the Anderson's Attack in a volunteer computing
project}\label{sec:boinc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In order to solve 10 cryptanalysis problems for the A5/1 keystream generator we
launched the volunteer computing project AndersonAttack@home. The computing
application of this project is based on the CUDA implementation, which was
described in the previous section.

Volunteer computing is a type of distributed computing which uses computational
resources of PCs (hosts) of private persons called volunteers. Each volunteer
computing project is designed to solve one or several hard problems. When PC is
connected to the project, all the calculations are performed automatically and
do not inconvenience user since only idle resources of PC are used. Volunteers
get credits (points) for each calculated task.

Volunteer computing project consists of the following basic parts: server
daemons, database, web site and client application. Daemons include
\textsc{work generator} (generates tasks to be processed), \textsc{validator}
(checks the correctness of the results received from volunteer's PCs) and
\textsc{assimilator} (processes correct results). Client application should
have versions for the widespread computing platforms.  One of attractive
features of volunteer computing is its low cost --- to maintain a project one
only needs a dedicated server working 24/7.

AndersonAttack@home is based on BOINC (Berkley Open Infrastructure for Network
Compuitng \cite{DANDERSON2004}), which is the most popular platform for
volunteer computing. Each BOINC-based project is separate, but any private
person can take part in arbitrary project with the help of standard BOINC
manager. This BOINC manager allows users to change projects priority and to
regulate the mode of PC using.

BOINC provides a form of redundant computing.  According to this, several (at
least 2) similar tasks are created for each workunit. These tasks are processed
on multiple hosts, the results are compared on a project server by validator,
and are accepted only when a 'consensus' is reached. The sufficient number of
successful results is called a 'quorum'. If for a particular workunit results
of tasks are nonsimilar, then new tasks must be created and sent. The scheme of
a BOINC-based project with the quorum of 2 is shown on the Fig. 1.

\begin{figure} \includegraphics[width=\linewidth]{./boinc.png}
	\caption{Simultaneous computation of $D$ instances of scheme $C(f)$ with
	bit-slicing technique} \label{fig:a51gen} 
\end{figure}

On the first stage of our experiment on AndersonAttack@home, a family of
workunits was generated on the project server. In each workunit values of 12
variable cells out of 53 (see the previous section) were fixed.  Thus, 40960
workunits were generated for 10 cryptanalysis instance in total. Usually the
value of deadline for workunits in BOINC projects is equal to 10-14 days. In
our project we used the deadline of 1 day, because the experiment was quite
small.  On the next stage all generated workunits were processed in a desktop
grid formed by project’s hosts. This took about 7 days. As a result, solutions
for all considered instances were successfully found. All these solutions are
listed in Table 1. It should be noted, that collisions were found for 7 out of
10 instances (5 of them have 1 collision, each of other 2 instances has 2
collisions).

\begin{table} \caption{} \label{tab:keys} Original secret keys and collisions of the
	generator A5/1 (in hexadecimal format) which were found in
	AndersonAttack@home.
	\begin {center} 
		\begin{tabular}
			{| l | l | l |}
			\hline
			Instance & Keystream & Secret key \\ \hline
			1 & 0x770c0410869366f1 & original 0x11b8e4340276c4ee \\
			  &                    & collision1 0x42634f3266d302a3 \\ \hline
			2 & 0xae9590560c26e9ed & original 0x4c656fd73e59ab9b \\
			  &                    & collision1 0xcf23e4722e3cfb68 \\ \hline
			3 & 0xdd4b3ab7f6cf8224 & original 0x09429d158555f4b3 \\
			  &                    & collision1 0x09429d158553e967 \\
			  &                    & collision2 0x40e5f2c8128a1781 \\ \hline
			4 & 0x93cd42d97eb75fd9 & original 0xfa386a338355aafd \\
			  &                    & collision1 0xf9e81096bb4d0aad \\ 
			  &                    & collision2 0xf9e81096bb4a8556 \\ \hline
			5 & 0x925e423c98121152 & original 0xe5cf81035ce5fbe2 \\ \hline
			6 & 0x3b3464bd6e377b87 & original 0x9625e9d810b46248 \\
			  &                    & collision1 0xf5aa1be2d6c36e18 \\ \hline
			7 & 0x0367d29121dd1677 & original 0xd1b8b06086edf162 \\ \hline
			8 & 0x6b49230b7fc0249d & original 0xbe81a896968c486b \\ \hline
			9 & 0xc65847556752d14c & original 0xb6f65d2855a211c0 \\ 
			  &                    & collision1 0xb6f65d2855a508e0 \\ \hline
			10& 0x07bb7f83d26072ec & original 0x122a1a2955286b9f \\ 
			  &                    & collision1 0xd5151aaa50490012 \\ \hline
		\end{tabular}
	\end {center}
\end{table}

Performance of the different implementations of the According to BOINC
statistics, 143 active hosts of 90 volunteers participated in the experiment.
Here by ‘active’ we mean a host which correctly processed at least one task.
Active volunteer has at least one active host. It should be noted, there is
only 1 volunteer from Russia in top-10 project volunteers list (formed
according to the amount of credits), the most of them are from United States (4
persons). In top-10 list of teams there is only one team from Russia too.
